Coupling finite and boundary element methods to solve the Poisson--Boltzmann equation for electrostatics in molecular solvation

### 2023-09-20 methods.tex
flipped names of equations in methods

The implicit solvent model\cite{RouxSimonson1999, DecherchiETal2015} can be described mathematically as a coupled system of partial differential equations, where the Poisson--Boltzmann equation governs in the solvent region ($\Omega_1$ in Figure \ref{fig:implicit_molecule}), and the Poisson equation governs in the solute region ($\Omega_2$ in Figure \ref{fig:implicit_molecule}). These regions are interfaced by the molecular surface ($\Gamma$), where the potential ($\phi$) and electric displacement ($\epsilon\partial\phi/\partial\mathbf{n}$) are continuous across the surface. The linearised Poisson-Boltzmann equation that results from approximating $\sinh(x)$ with $x$ follows
%
\begin{subequations}
\label{eq:pbe}
\begin{align}
\nabla^2\phi_1(\mathbf{x}) &= \tfrac{1}{\epsilon_1}\sum_{k=1}^{N_q} q_k\delta(\mathbf{x},\mathbf{x}_k)&&\mathbf{x} \in \Omega_1,\label{eq:pbe1}\\
\left(\nabla^2 - \kappa^2\right)\phi_2(\mathbf{x})  &= 0&&\mathbf{x}\in\Omega_2,\label{eq:pbe2}\\
\phi_1(\mathbf{x})  &= \phi_2 (\mathbf{x}),&&\mathbf{x}\in \Gamma,\label{eq:pbe3}\\
\epsilon_1\frac{\partial\phi_1}{\partial\mathbf{n}}(\mathbf{x}) &= \epsilon_2\frac{\partial\phi_2}{\partial\mathbf{n}}(\mathbf{x})&&\mathbf{x}\in \Gamma. \label{eq:pbe4}
\end{align}
\end{subequations}
%
Here, $\epsilon_1$ and $\epsilon_2$ are the dielectric constants in the solute and solvent, respectively; $\kappa$ is the inverse of the Debye length, related to the salt concentration; and $q_k$ are the values of the partial charges, located at $\mathbf{x}_k$.

>>>>

The implicit solvent model\cite{RouxSimonson1999, DecherchiETal2015} can be described mathematically as a coupled system of partial differential equations, where the Poisson equation governs in the solvent region ($\Omega_1$ in Figure \ref{fig:implicit_molecule}), and the Poisson--Boltzmann equation governs in the solute region ($\Omega_2$ in Figure \ref{fig:implicit_molecule}). These regions are interfaced by the molecular surface ($\Gamma$), where the potential ($\phi$) and electric displacement ($\epsilon\partial\phi/\partial\mathbf{n}$) are continuous across the surface. The linearised Poisson-Boltzmann equation that results from approximating $\sinh(x)$ with $x$ follows
%
\begin{subequations}
\label{eq:pbe}
\begin{align}
\nabla^2\phi_1(\mathbf{x}) &= \tfrac{1}{\epsilon_1}\sum_{k=1}^{N_q} q_k\delta(\mathbf{x},\mathbf{x}_k)&&\mathbf{x} \in \Omega_1,\label{eq:pbe1}\\
\left(\nabla^2 - \kappa^2\right)\phi_2(\mathbf{x})  &= 0&&\mathbf{x}\in\Omega_2,\label{eq:pbe2}\\
\phi_1(\mathbf{x})  &= \phi_2 (\mathbf{x}),&&\mathbf{x}\in \Gamma,\label{eq:pbe3}\\
\epsilon_1\frac{\partial\phi_1}{\partial\mathbf{n}}(\mathbf{x}) &= \epsilon_2\frac{\partial\phi_2}{\partial\mathbf{n}}(\mathbf{x})&&\mathbf{x}\in \Gamma. \label{eq:pbe4}
\end{align}
\end{subequations}
%
Here, $\epsilon_1$ and $\epsilon_2$ are the dielectric constants in the solute and solvent, respectively; $\kappa$ is the inverse of the Debye length, related to the salt concentration; and $q_k$ are the values of the partial charges, located at $\mathbf{x}_k$.
